---
title: "Results from Identity Alignement on Atitude and Affect"
author: "Alina Gutoreva"
date: "3 August 2018"
output: word_document
---

```{r, echo = FALSE, message = FALSE, comment = NA}
knitr::opts_chunk$set(echo = TRUE)
```

## Results from Identity Alignement on Atitude and Affect

In this study, there were two factors with two levels each, making up four different groups. First factor, is alignement - alignened social identity or misaligned. Second factor was valence of the identity - concerned and unconcerned.
There were 7 different measures in this study all measured within each participant:

Attitude:
  1. Positive Attitude change
  2. Negativr Attitude change
  3. Overall Attitude change
  
Affect :
  4. Positive Affect change
  5. Negative Affect change
  6. Overall Affect change
  
7. Belief change

And other more explorative measures such as
8. Economic behaviour (Dictator's game 'playing' with the social source)
9. Trustworthiness of social source
10. Ethical 
11. Reliability of information provided by social source

Additional measures are social desirability and ethical viewpoints.


```{r, echo = FALSE, message = FALSE, comment = NA}
library(data.table)
id_data <- fread("file:///C:/Users/u1664328/Dropbox/4. Work with Sebastiano/Attitude and Emotion study/Data/Importnat - Data/data_for_r.csv",header=T)
View(id_data)
id_data <- id_data[,c(-1,-2)] # deleting participant id row
id_data$condition <- as.factor(id_data$condition)
id_data$alignement <- as.factor(id_data$alignement)
levels(id_data$alignement) <- c("misaligned", "aligned")
```

## Data included in the analysis

The were two exclusion criteria based on whether subjects read the text provided by the social source and in one of the affect questionnaires. In this analysis, participants who failed the first 'check' question were also included due to a low number of participants who hold negative valence of identity factor. This, however, might be change in upcoming analysis.

## Plots

```{r, echo = FALSE, message = FALSE, comment = NA}
#proportion risky across lotteries
library(dplyr)
library(knitr)
summary <- id_data %>% 
  group_by(condition, alignement) %>%
  summarize_all(funs(mean))

View(id_data)
head(summary)
```

The sumamry of the data based on condition is as follows.

# Attitude

### Total Attitude Change
```{r, echo = FALSE, message = FALSE, comment = NA}
library(ggplot2)
#a function to get rid of the ugly grey background in ggplot2
cleanup = theme(panel.grid.major  = element_blank(),
                panel.grid.minor  = element_blank(),
                panel.background  = element_blank(),
                axis.line = element_line(color = "black"))

att_total = ggplot(id_data, aes(x=condition, y=change_total_attit, fill=alignement)) +  geom_violin()
att_total +
  stat_summary(fun.y=mean, geom="point", 
               shape=23, size=2, 
               color="black")+
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.2)+
  cleanup +
  ylim(0, 100) +
  xlab("Condition")+
  ylab("Total Attitude Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))



#Bar plot
att_total_bar = ggplot(id_data, aes(condition, change_total_attit,fill=alignement)) # creating a blank plot

att_total_bar +
  stat_summary(fun.y = mean, geom = "bar", 
               fill = "grey", 
               color = "black") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  cleanup +
  ylim(0, 100) +
  xlab("Condition")+
  ylab("Total Attitude Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))




ggplot(id_data, aes(x=condition, y=change_total_attit, fill=alignement)) +
    geom_boxplot(alpha=0.4) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=10, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set3")+
    cleanup +
    ylim(0, 100) +
    xlab("Condition")+
    ylab("Total Attitude Change")+
    scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))
```

Test between the conditions - aligned vs. misaligned
```{r, echo = FALSE, message = FALSE, comment = NA}
#analysis
t.test(change_total_attit ~ alignement, id_data, paired=FALSE,var.equal=TRUE)
```
ANOVA test between all four groups
```{r, echo = FALSE, message = FALSE, comment = NA}

##realised that we need to change condition to a factor with two levels = valence of "concerned" and "unconcerned"
# so, for analysis use a different data
id_data$valence<-id_data$condition
id_data$valence <- as.factor(id_data$valence)
levels(id_data$valence) <- c("concerned", "concerned", "unconcerned", "unconcerned")

res.aov2 <- aov(change_total_attit ~ valence + alignement, data = id_data)
summary(res.aov2)

```




### Positive Attitude Change

```{r, echo = FALSE, message = FALSE, comment = NA}
library(ggplot2)
#a function to get rid of the ugly grey background in ggplot2
att_pos = ggplot(id_data, aes(x=condition, y=change_pos_attit, fill=alignement)) +  geom_violin()
att_pos +
  stat_summary(fun.y=mean, geom="point", 
               shape=23, size=2, 
               color="black")+
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.2)+
  cleanup +
  ylim(0, 100) +
  xlab("Condition")+
  ylab("Positive Attitude Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))



#Bar plot
att_pos_bar = ggplot(id_data, aes(condition, change_pos_attit,fill=alignement)) # creating a blank plot

att_pos_bar +
  stat_summary(fun.y = mean, geom = "bar", 
               fill = "grey", 
               color = "black") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  cleanup +
  ylim(0, 100) +
  xlab("Condition")+
  ylab("Positive Attitude Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))




ggplot(id_data, aes(x=condition, y=change_pos_attit, fill=alignement)) +
    geom_boxplot(alpha=0.4) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=10, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set3")+
    cleanup +
    ylim(0, 100) +
    xlab("Condition")+
    ylab("Positive Attitude Change")+
    scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))
```

Test between the conditions - aligned vs. misaligned
```{r, echo = FALSE, message = FALSE, comment = NA}
#analysis
t.test(change_pos_attit ~ alignement, id_data, paired=FALSE,var.equal=TRUE)
```
ANOVA test between all four groups
```{r, echo = FALSE, message = FALSE, comment = NA}
res.aov2 <- aov(change_pos_attit ~ valence + alignement, data = id_data)
summary(res.aov2)
```

### Negative Attitude Change

```{r, echo = FALSE, message = FALSE, comment = NA}
library(ggplot2)
#a function to get rid of the ugly grey background in ggplot2
att_neg = ggplot(id_data, aes(x=condition, y=change_neg_attit, fill=alignement)) +  geom_violin()
att_neg +
  stat_summary(fun.y=mean, geom="point", 
               shape=23, size=2, 
               color="black")+
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.2)+
  cleanup +
  ylim(0, 100) +
  xlab("Condition")+
  ylab("Negative Attitude Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))



#Bar plot
att_neg_bar = ggplot(id_data, aes(condition, change_neg_attit,fill=alignement)) # creating a blank plot

att_neg_bar +
  stat_summary(fun.y = mean, geom = "bar", 
               fill = "grey", 
               color = "black") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  cleanup +
  ylim(0, 100) +
  xlab("Condition")+
  ylab("Negative Attitude Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))




ggplot(id_data, aes(x=condition, y=change_neg_attit, fill=alignement)) +
    geom_boxplot(alpha=0.4) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=10, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set3")+
    cleanup +
    ylim(0, 100) +
    xlab("Condition")+
    ylab("Negative Attitude Change")+
    scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))
```

Test between the conditions - aligned vs. misaligned
```{r, echo = FALSE, message = FALSE, comment = NA}
#analysis
t.test(change_neg_attit ~ alignement, id_data, paired=FALSE,var.equal=TRUE)
```

ANOVA test between all four groups
```{r, echo = FALSE, message = FALSE, comment = NA}
res.aov2 <- aov(change_neg_attit ~ valence + alignement, data = id_data)
summary(res.aov2)
```

#Affect

###Total Affect Change
```{r, echo = FALSE, message = FALSE, comment = NA}
library(ggplot2)
#a function to get rid of the ugly grey background in ggplot2
aff_total = ggplot(id_data, aes(x=condition, y=change_total_aff, fill=alignement)) +  geom_violin()
aff_total +
  stat_summary(fun.y=mean, geom="point", 
               shape=23, size=2, 
               color="black")+
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.2)+
  cleanup +
  ylim(0, 3) +
  xlab("Condition")+
  ylab("Total Affect Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))



#Bar plot
aff_total_bar = ggplot(id_data, aes(condition, change_total_aff, fill=alignement)) # creating a blank plot

aff_total_bar +
  stat_summary(fun.y = mean, geom = "bar", 
               fill = "grey", 
               color = "black") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  cleanup +
  ylim(0, 3) +
  xlab("Condition")+
  ylab("Total Affect Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))


#boxplot
ggplot(id_data, aes(x=condition, y=change_total_aff, fill=alignement)) +
    geom_boxplot(alpha=0.4) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=10, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set3")+
    cleanup +
    ylim(0, 3) +
    xlab("Condition")+
    ylab("Total Affect Change")+
    scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))
```

Test between the conditions - aligned vs. misaligned
```{r, echo = FALSE, message = FALSE, comment = NA}
#analysis
t.test(change_total_aff ~ alignement, id_data, paired=FALSE,var.equal=TRUE)
```

ANOVA test between all four groups
```{r, echo = FALSE, message = FALSE, comment = NA}
res.aov2 <- aov(change_total_aff ~ valence + alignement, data = id_data)
summary(res.aov2)
```


###Positive Affect Change

```{r, echo = FALSE, message = FALSE, comment = NA}
library(ggplot2)
#a function to get rid of the ugly grey background in ggplot2
aff_pos = ggplot(id_data, aes(x=condition, y=change_pos_aff, fill=alignement)) +  geom_violin()
aff_pos +
  stat_summary(fun.y=mean, geom="point", 
               shape=23, size=2, 
               color="black")+
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.2)+
  cleanup +
  ylim(0, 3) +
  xlab("Condition")+
  ylab("Positive Affect Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))



#Bar plot
aff_pos_bar = ggplot(id_data, aes(condition, change_pos_aff, fill=alignement)) # creating a blank plot

aff_pos_bar +
  stat_summary(fun.y = mean, geom = "bar", 
               fill = "grey", 
               color = "black") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  cleanup +
  ylim(0, 3) +
  xlab("Condition")+
  ylab("Positive Affect Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))


#boxplot
ggplot(id_data, aes(x=condition, y=change_pos_aff, fill=alignement)) +
    geom_boxplot(alpha=0.4) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=10, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set3")+
    cleanup +
    ylim(0, 3) +
    xlab("Condition")+
    ylab("Positive Affect Change")+
    scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))
```
Test between the conditions - aligned vs. misaligned
```{r, echo = FALSE, message = FALSE, comment = NA}
#analysis
t.test(change_pos_aff ~ alignement, id_data, paired=FALSE,var.equal=TRUE)
```

ANOVA test between all four groups
```{r, echo = FALSE, message = FALSE, comment = NA}
res.aov2 <- aov(change_pos_aff ~ valence + alignement, data = id_data)
summary(res.aov2)
```

### Negative Affect Change

```{r, echo = FALSE, message = FALSE, comment = NA}
library(ggplot2)
#a function to get rid of the ugly grey background in ggplot2
aff_neg = ggplot(id_data, aes(x=condition, y=change_neg_aff, fill=alignement)) +  geom_violin()
aff_neg +
  stat_summary(fun.y=mean, geom="point", 
               shape=23, size=2, 
               color="black")+
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.2)+
  cleanup +
  ylim(0, 3) +
  xlab("Condition")+
  ylab("Negative Affect Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))



#Bar plot
aff_neg_bar = ggplot(id_data, aes(condition, change_neg_aff, fill=alignement)) # creating a blank plot

aff_neg_bar +
  stat_summary(fun.y = mean, geom = "bar", 
               fill = "grey", 
               color = "black") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  cleanup +
  ylim(0, 3) +
  xlab("Condition")+
  ylab("Negative Affect Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))


#boxplot
ggplot(id_data, aes(x=condition, y=change_neg_aff, fill=alignement)) +
    geom_boxplot(alpha=0.4) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=10, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set3")+
    cleanup +
    ylim(0, 3) +
    xlab("Condition")+
    ylab("Negative Affect Change")+
    scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))
```

Test between the conditions - aligned vs. misaligned
```{r, echo = FALSE, message = FALSE, comment = NA}
#analysis
t.test(change_neg_aff ~ alignement, id_data, paired=FALSE,var.equal=TRUE)
```

ANOVA test between all four groups
```{r, echo = FALSE, message = FALSE, comment = NA}
res.aov2 <- aov(change_neg_aff ~ valence + alignement, data = id_data)
summary(res.aov2)
```



# Belief change

```{r, echo = FALSE, message = FALSE, comment = NA}
library(ggplot2)
#a function to get rid of the ugly grey background in ggplot2
belief = ggplot(id_data, aes(x=condition, y=belief_change, fill=alignement)) +  geom_violin()
belief +
  stat_summary(fun.y=mean, geom="point", 
               shape=23, size=2, 
               color="black")+
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.2)+
  cleanup +
  ylim(0, 50) +
  xlab("Condition")+
  ylab("Belief Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))



#Bar plot
belief_bar = ggplot(id_data, aes(condition, belief_change, fill=alignement)) # creating a blank plot

belief_bar +
  stat_summary(fun.y = mean, geom = "bar", 
               fill = "grey", 
               color = "black") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", width = .2, 
               position = "dodge") +
  cleanup +
  ylim(0, 50) +
  xlab("Condition")+
  ylab("Belief Change")+
  scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))


#boxplot
ggplot(id_data, aes(x=condition, y=belief_change, fill=alignement)) +
    geom_boxplot(alpha=0.4) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=10, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set3")+
    cleanup +
    ylim(0, 50) +
    xlab("Condition")+
    ylab("Belief Change")+
    scale_x_discrete(labels=c("Aligned\nConcerned", "Misaligned\nConcerned","Aligned\nUnconcerned", "Misaligned\nUnconcerned"))
```

Test between the conditions - aligned vs. misaligned
```{r, echo = FALSE, message = FALSE, comment = NA}
#analysis
t.test(belief_change ~ alignement, id_data, paired=FALSE,var.equal=TRUE)
```

ANOVA test between all four groups
```{r, echo = FALSE, message = FALSE, comment = NA}
res.aov2 <- aov(belief_change ~ valence + alignement, data = id_data)
summary(res.aov2)
```